Preprocessing datasets

### 2020-05-13 datasets/readme.Rmd
update research archive

---
title: "Dataset preprocessing"
output: github_document
---
This notebook processes all systematic review datasets into datasets suitable testing ASReview.

@@

Entries with missing abstracts are removed

>>>>

---
title: "Preprocessing datasets"
output: github_document
---

This notebook processes six systematic review datasets into datasets suitable for simulating the screening process.

- Wilson - [@Appenzeller-Herzog2020] is on a review on effectiveness and safety of treatments of Wilson Disease, a rare genetic disorder of copper metabolism [@Appenzeller-Herzog2019]. 
- Ace -  contains publications on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors, a drug treatment for heart disease [@Cohen2006]. 
- Virus -  is from a systematic review on studies that performed viral Metagenomic Next-Generation Sequencing (mNGS) in farm animals [@Kwok2020]. 
- Software - from the software engineering field, contains publications on fault prediction in source code [@Hall2012].
- Nudging dataset - [@Nagtegaal2019a] on nudging healthcare professionals [@Nagtegaal2019], stemming from the area of 
- PTSD - on studies applying latent trajectory analyses on posttraumatic stress after exposure to traumatic events [@vandeSchoot2017].

Data were preprocessed from their original source into a test dataset, containing title and abstract of the publications obtained in the initial search. Candidate studies with missing abstracts and duplicate instances were removed from the data.

Every dataset has 2 versions: one for hyperparameter optimization `test_datasets` and one for simulation `sim_datasets`.

@@
